Borders and Gateways: Measuring and Analyzing National AS Chokepoints

### 2018-07-31 Paper/related.tex
Jed added a paragraph to the end of related.tex

>>>>

While there have been attempts to systematize different technical approaches to
censoring Internet content~\cite{Tschantz2016a,Khattak2016a} there is no
comprehensive list of all the different ways a state actor can manipulate
traffic.  For some methods the AS graph is relevant, such as IP address
blacklisting, traffic throttling~\cite{DBLP:journals/corr/Anderson13}, URL or
packet filtering, packet injection, physically shutting down infrastructure, and
BGP attacks.  For other methods the AS graph is less relevant, such as creating
internal national networks~\cite{DBLP:journals/corr/abs-1209-6398}, portal
censorship such as search engine filtering and social media post deletion,
propaganda campaigns, and manipulation of the DNS system.  Our work is
complementary to other studies that focus more on Internet routing's effect on
high-level content than on a country's desire to enforce policies on all traffic
that crosses their borders, such as Edmundson \emph{et
al.}~\cite{Edmundson:2018:NHI:3209811.3211887}.
